\begin{longtable} { | c | c | p{5cm} | p{5cm} | c | } 
\hline
	ID 	&	Iced	&	Issues	&	Description		&	 Es. hours \\\hline
	21	& 	 	&	View-mode created	& 	Blur pictiures out of focus. Only full pictures(no half/auto adjust). Marker-choice: arrow or highlight, locked or dynamic position of marker. Possible settings for up to 7 pictograms.	&	128 hours	\\\hline
	22	& 	x	&	Portrait mode	& 	The sequences should be viewable in portrait mode.	&	32 hours	\\\hline
	23	& 	 	&	SequenceGrid needs to be dynamic	& 	Right now, SequenceGrid only allows 4 pictograms in the Grid.	&	8 hours	\\\hline
	24	& 	 	&	Delete sequences	& 	Delete sequences requires database syncronization, with the LocalDB.	&	2 hours	\\\hline
	25	& 	x	&	Fix ADD/SAVE/BACK button in SequenceActivity	& 	Currently blocked because it is not possible to save sequences (Missing database functionality).	&	4 hours	\\\hline
	26	& 	 	&	Change all buttons	& 	The new GUI buttons are available in the wiki for GUI.	&	8 hours	\\\hline
	27	& 	 	&	Change GUI of Viewgroups	& 	The new GUI Viewgroups are available in the wiki for GUI.	&	16 hours	\\\hline
	28	& 	 	&	Remove the Childlist	& 	Update and adapt to context, because child is sent from Launcher.	&	32 hours	\\\hline
	29	& 	 	&	Update to Oasis	& 	Update to the new database.	&	4 hours \\\hline
	30  & 	 	&	Refactor overview	& 	Create BaseOverview. Create GuardianOverview.	&	32 hours	\\\hline
	31  & 	 	&	Rework sequenceTitle box to look editable	& 	If we can make it look clickable we can remove the button.	&	4 hours	\\\hline
	32  & 	 	&	Display some temporary sequences in overview	& 	Since there is no database for sequences yet, we need to be able to display some temporary ones for development purposes	&	4 hours	\\\hline
	33	&	& 	Nested Sequences	&	There is a need for nested sequences, similar to daily scheduel (self-explanatory)	& 	64 hours   \\\hline
	34	&	&	Choices in Sequences		&	Implement sequences so that they can contain the option to make choices.	& 	16 hours  \\\hline
	35	&	&	After adding pictograms to a sequence it should not go to the "sequenceActivity", it should go to "MainActivity"		&	After making a sequence, the application should load the overview, instead of loading the sequence in SequenceActivity.	& 	8 hours  \\\hline
\caption{This is a list of the issues we had in our product backlog going into sprint 2}
\label{tab:spr2_prodblog}
\end{longtable}

