\begin{longtable} { | c | c | p{5cm} | p{5cm} | c | } 
\hline
	ID 	& Iced	&	Issues	&	Description		&	 Es. hours \\\hline
	63	& 		& 	Sequenceviewer: Display nested sequences	&	Should be able to display nested sequences		& 	16 hours \\\hline
	64	& 		&   Sequenceviewer: Display choice	&	Requirement from the Sequence-group and the Lifestories-group	& 	16 hours  \\\hline
	65	& 		& 	Sequenceviewer: Play/pause/stop sound	&	Requirement for the Parrot-group.	& 	32 hours  \\\hline
	66	& 		& 	Sequenceviewer: DB sync	&	Gather all the information through sequenceID as you can not send a sequence as intent			 &  32 hours \\\hline
	67	& 		& 	Sequenceviewer: Portrait-mode	&	Supporting portrait mode - reading sequences from top and down	&   2 hours \\\hline
	68	&		& 	Sequenceviewer: Landscape-mode	&	Supporting landscape mode - reading sequences from left to right		& 		   2 hours \\\hline
	69	& 		& 	Sequenceviewer: Marker drag over to next pictogram	&	Being able to drag the marker to the next pictogram in a sequence	& 	16 hours	   \\\hline
	70	& 		& 	Sequenceviewer: Marker stays at pictogram when scrolling the sequence	&	Being able to to snap the marker to a pictogram, not changing what is points to when scrolling the sequence.		& 	8 hours	   \\\hline
	71	& 		& 	Sequenceviewer: Marker snaps to pictogram	&	Snap-effect to the marker, when you you drag marker to a new pictogram.	& 		16 hours   \\\hline
	72	& 		& 	Sequenceviewer: 2 rows/columns. 1 with a marker, 1 with a sequence	&	Requirement from Lifestories-group.	& 	16 hours	   \\\hline
	73	& 		& 	Sequenceviewer: display 2 rows/columns	&	Requirement from Lifestories-group. They wanted two sequences to be displayed, one on top of the other.	& 	16 hours	   \\\hline
	74	& 		& 	Sequenceviewer: While playing sound, follow the pictogram which has sound being played	&	When playing sound, a marker should highlight the pictogram with sound being played at that moment, following along the sequence when playing it all.	& 		32 hours   \\\hline
\caption{This is a list of the issues all related to sequenceviewer}
\label{tab:spr4_sw_prodblog}
\end{longtable}

