\subsection{Remaining Issues}\label{subsec:remain_issues}
The following is the remaining issues not completed within the time-frame for sprint 1.

\begin{longtable} { | c | p{12cm} | c | } 
\hline
	ID 	&	Issues	&		 Es. hours \\\hline
	2	&	Updating a picture in sequence -$>$; no update in overview	&	8 hours	\\\hline
	\caption{Issue ID 2}
\label{tab:spr1_overviewupdate}
\end{longtable}
This was an issue that we did not look into, because of time-limitations. The reason this particular issue has been pushed back in favor of others was both because it was not a high priority issue and because having pictograms in Sequence was a prerequisite, refer issue 14 in table \ref{tab:spr1_issue14}. 

\begin{longtable} { | c | p{12cm} | c | } 
\hline
	ID 	&	Issues	&		 Es. hours \\\hline
	4	&	Home button pauses sequence -$>$ should destroy 	&	8 hours	\\\hline
	\caption{Issue ID 4}
\label{tab:spr1_homebtndestroy}
\end{longtable}

According to the previous report on Sekvens\citep{Zebra}, the home button caused an issue. After using the homebutton, the guardian found it confusing when reopening Sequence, it resumed at the previous state of the application. It was preferred that the application should reopen as if it was just launched. This issue was looked into and an attempt to solve it was made by destroying the application when the home button was pressed. This however caused a new bug where Sequence would be destroyed after accessing PictoSearch from the application. The proposed solution was thus discarded.