\subsection{Cat: applying feedback from `Sekvens'}\label{subsec:collab_catresult}
Several changes were made to the class \ct{MainActivity} as a result of the feedback from sw607f14.

\paragraph{Adapters:}
In several places we created and set new adapters to update the GUI. This was changed to use the \ct{notifyDataSetChanged} method instead. In some places however, this did not work, and we were thus forced to set the adapters again.

\paragraph{Controllers:}
Instead of instantiating our own instances of the necessary controllers, we switched to use the \ct{Helper} class from Oasis. This made some lines a bit longer, but was otherwise worth it. In the process, we also removed all usage of \ct{CategoryLib}, although it was not removed as neither a submodule or from git.

\paragraph{Dialogs:}
Instead of calling \ct{cancel} on dialogs when they were closed, we now call \texttt{dismiss}.

\paragraph{\ct{onPause} method:}
As the \ct{onPause} method was unneeded, it was removed. It had been used before when Cat was using XML files to store its data, but only the code handling this had been removed.

\paragraph{Contrived complexity and complex conditionals:}
As was noted, we had some cases of complex conditionals. The \ct{OnActivityResult} method was the worst in this. Before refactoring the method, it consisted of several if-statements (some of which made a ``backwards'' check, e.g.\ \ct{if (isIcon != true) \{ \ldots{} \}}). After refactoring, the method contained a switch statement, with four cases, which is much easier to read.

\paragraph{Rejected suggestions:}
Other suggestions for improving the code was rejected simply due to a lack of time.