
\begin{longtable} { | c | c | p{5cm} | p{5cm} | c | }
\hline
	ID 	&	Iced	&	Issues	&	Description		&	 Es. hours \\\hline
	1	& 	x	&	Syncronization with the Database		& 	Work together with the Database group to correctly link Sequence with the database - making extracting and saving images easier.	&	32 hours	\\\hline
	2	& 	x	&	Updating a picture in sequence -\&gt; no update in overview	&	When opdating a picture in sequence, the picture is not shown in the overview.	&	8 hours	\\\hline
	3	& 		&	Cancel and replace action function	&	Being able to mark a pictogram cancelled. Futhermore being able to replace pictograms in a sequence	&	12 hours \\\hline
	4	& 		&	Home button pauses sequence -$>$ should destroy	 &	When pressing the home button on the tablet, it should destroy the application, and not pause it. For example it would be confusing, to open from paused state, instead of opening into the overview.	&	8 hours.	\\\hline
	5	& 		&	Copying Sequences	&	Being able to copy sequences to other children incase of similar activities	&	16 hours \\\hline
	6	& 		&	Changing name	&	Change the name from Zebra to something else.	&	1 hour	\\\hline
	7	& 		&	Marked pictogram not highlighted		&	When the pictogram is clicked it does not highlight.	&	8 hours 	\\\hline
	8	& 		&	Child mode needs to be more intuitive		&	Child mode relies on scrolling right now - we need to make it more intutive e.g. marked activities/pictograms as done. Overall the flow of child mode needs to be reworked	&	32 hours	\\\hline
	9	& 		&	Sequence does not look clickable		&	It is hard to see that you can click a sequence and choose to "open" it.	&	16 hours	\\\hline
	10	& 		&	Changing name is not intuitive	&	When naming a sequence it is hard to see that you can click on the "space" to name it.	&	8 hours	\\\hline
	11	& 		&	Analyzing TODOs in code	&	The TODO's are located in: Child (class), MainActivity and SequenceViewGroup - Note there can be several TODO's per file		&	16 hours	\\\hline
	12	& 		&	Add sequence button placement is not intuitive	&	The "+" sign is wrongly placed	&	16 hours 	\\\hline
	13	& 		&	Resizing delete buttons on pictograms	&	The size of the deletebutton have to scale proportionally with the width of the PictogramView.	&	4 hours	\\\hline
	14	& 	x	&	Loading pictures in Sequence	&	Right now, no pictures are visible in the program right now	&	4 hours	\\\hline
	15	& 		&	Original drag location flickers when rearranging	&	When dragging the location dragged from flickers when the animation is done. Comment from last semester: Seems to be depend on hardware. The old galaxy tab does not have this problem. Also seems to be worsened by rounded image corners	&	32 hours 	\\\hline
	16	& 		&	It is possible to make identical sequences for the same child	&	Should be fixed, maybe as a check vs name and order of pictograms.	&	8 hours	\\\hline
	17	& 	x	&	Solve TODO in SequenceViewGroup - Can child be bigger than parent?	&	It is currently unknown whether a child can be bigger than the parent space allowed. Blocked because no images are available yet.	&	2 hours	\\\hline
	18	& 		&	Child selected upon opening the program is not highlighted	&	Child selected upon opening the program is not highlighted - starts at the first child of the list but it is not highlighted	&	2 hours	\\\hline

\end{longtable}




\paragraph{Code-mapping}
\emph{Description} : Map the code - to understand fully.\\
\emph{Estimated hours}: 8 hours.
\paragraph{Name-change}
\emph{Description} : Chance the name from Zebra to something else and change the logo from a zebra to something else.\\
\emph{Estimated hours}: 1 hour.
\paragraph{Analyzing TODOs}
\emph{Description} : The TODO's are located in: Child (class), MainActivity and SequenceViewGroup - Note there can be several TODO's per file. \\
\emph{Estimated hours}: 16 hours.
\paragraph{Return button in Sequence Activity needed}
\emph{Description} : When a sequences is created it should have a return to overview button, right now it's still in the sequence view - the hardware button works, but it is not intuitive.\\
\emph{Estimated hours}: 8 hours.
\paragraph{Loading pictures in Sequence}
\emph{Description} : Right now, no pictures are visible in the program. It is hard to test when there is no visual effect.\\
\emph{Estimated hours}: 4 hours.\\
\emph{Special status} : Blocked until the database group has uploaded their program.
\paragraph{Highlighting child upon launch/return of Main activity}
\emph{Description} : The first child should be highlighted when launching the program - as the sequences belonging to the child already are present. The same thing applies when returning from another activity.\\
\emph{Estimated hours}: 2 hours.
\paragraph{Zebra is installed twice}
\emph{Description:} Solved but not changed - This is due to this line in the pictogram-lib Manifesto: 
$<$category android:name="android.intent.category.LAUNCHER" /$>$ 
Deleting the line fixes the problem and causes no other problems by the look of it. We however have no rights to push on pictogram-lib.\\
\emph{Estimated hours} : 16 hours.
\paragraph{Report review}
\emph{Description} : Locate the issues from the old report and write them down in our report.\\
\emph{Estimated hours}: 8 hours.
\paragraph{Making structure for the report}
\emph{Description} : Making a structure for the report - setting it up with Git.\\
\emph{Estimated hours}: 8 hours.
\paragraph{Updating the picture in Sequence -> doesn't update in overview}
\emph{Description} : When opdating a picture in sequence, the picture is not shown in the overview. \\
\emph{Estimated hours}: 8 hours.\\
\emph{Special status} : Blocked until \emph{Loading pictures in Sequence} is fixed.
\paragraph{Home button pauses sequence -> should destroy}
\emph{Description} : When pressing the home button on the tablet, it should destroy the application, and not pause it. For example it would be confusing, to open from paused state, instead of opening into the overview. \\
\emph{Estimated hours}: 8 hours.