\subsection{Issues}

\paragraph{Code-mapping}
\emph{Description} : Map the code - to understand fully.\\
\emph{Estimated hours}: 8 hours.
\paragraph{Name-change}
\emph{Description} : Chance the name from Zebra to something else and change the logo from a zebra to something else.\\
\emph{Estimated hours}: 1 hour.
\paragraph{Analyzing TODOs}
\emph{Description} : The TODO's are located in: Child (class), MainActivity and SequenceViewGroup - Note there can be several TODO's per file. \\
\emph{Estimated hours}: 16 hours.
\paragraph{Return button in Sequence Activity needed}
\emph{Description} : When a sequences is created it should have a return to overview button, right now it's still in the sequence view - the hardware button works, but it is not intuitive.\\
\emph{Estimated hours}: 8 hours.
\paragraph{Loading pictures in Sequence}
\emph{Description} : Right now, no pictures are visible in the program. It is hard to test when there is no visual effect.\\
\emph{Estimated hours}: 4 hours.\\
\emph{Special status} : Blocked until the database group has uploaded their program.
\paragraph{Highlighting child upon launch/return of Main activity}
\emph{Description} : The first child should be highlighted when launching the program - as the sequences belonging to the child already are present. The same thing applies when returning from another activity.\\
\emph{Estimated hours}: 2 hours.
\paragraph{Zebra is installed twice}
\emph{Description:} Solved but not changed - This is due to this line in the pictogram-lib Manifesto: 
$<$category android:name="android.intent.category.LAUNCHER" /$>$ 
Deleting the line fixes the problem and causes no other problems by the look of it. We however have no rights to push on pictogram-lib.\\
\emph{Estimated hours} : 16 hours.
\paragraph{Report review}
\emph{Description} : Locate the issues from the old report and write them down in our report.\\
\emph{Estimated hours}: 8 hours.
\paragraph{Making structure for the report}
\emph{Description} : Making a structure for the report - setting it up with Git.\\
\emph{Estimated hours}: 8 hours.
\paragraph{Updating the picture in Sequence -> doesn't update in overview}
\emph{Description} : When opdating a picture in sequence, the picture is not shown in the overview. \\
\emph{Estimated hours}: 8 hours.\\
\emph{Special status} : Blocked until \emph{Loading pictures in Sequence} is fixed.
\paragraph{Home button pauses sequence -> should destroy}
\emph{Description} : When pressing the home button on the tablet, it should destroy the application, and not pause it. For example it would be confusing, to open from paused state, instead of opening into the overview. \\
\emph{Estimated hours}: 8 hours.